Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-10-25 paper/ms.tex

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_v_ige.pdf}
\caption{\label{fig:conversion}
Estimated yield of \Ni{56} as a function of final mass burned to IGE
for C-O-Ne progenitors (blue) and C-O progenitors (red) at
$t = 4.0 \second$.  Lines indicate corresponding relations found in W16 with
a lower central density and C-O-Ne progenitor whose interior is not mixed
during cooling.
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations.
The difference between the two sets of results is more pronounced
than the difference between C-O-Ne and C-O models found by \citet{willcoxetal2016}.
The results found here, in which the carbon-poor compositions have a lower fractional \Ni{56} yield, are more consistent with the expectation for a lower peak burning temperature with lower C abundance.
This motivates a closer inspection of how the \Ni{56}/IGE ratio evolves during the explosion.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_v_ige.pdf}
\caption{\label{fig:conversion}
Estimated yield of \Ni{56} as a function of final mass burned to IGE
for C-O-Ne progenitors (blue) and C-O progenitors (red) at
$t = 4.0 \second$.  Lines indicate corresponding relations found in 
\cite{willcoxetal2016} with
a lower central density and C-O-Ne progenitor whose interior is not mixed
during cooling.
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations.
The difference between the two sets of results is more pronounced
than the difference between C-O-Ne and C-O models found by \citet{willcoxetal2016}.
The results found here, in which the carbon-poor compositions have a lower fractional \Ni{56} yield, are more consistent with the expectation for a lower peak burning temperature with lower C abundance.
This motivates a closer inspection of how the \Ni{56}/IGE ratio evolves during the explosion.
